A Tutorial on Tailored Simulation-Based Sample Size Planning for Experimental Designs with Generalized Linear Mixed Models

### 2024-07-01 manuscript.qmd
fix subsection formatting; fix some names and double reference in bibfile; fix step 7 section name; add whitespace before table 2 in pdf

To our knowledge, existing approaches for sample size planning for GLMMs have exclusively focused on planning for power. In Table 1, we review available software packages that can be used to perform power analysis for multilevel models in `r cite_r()`. Power analysis methods can be categorized into formula-based, summary-statistics-based and simulation-based methods [@murayamaSummarystatisticsbasedPowerAnalysis2022]. Formula-based methods rely on exact formulas to calculate power directly. Summary-statistics-based methods use statistical theory to approximate power based on formula-based methods developed for simple t-tests. Simulation-based methods rely on repeatedly simulating data with a known true effect size and estimating power empirically, that is what percentage of simulated datasets produces a significant p-value.
Available formula-based and summary-statistics-based software packages for multilevel models often do not include GLMMs or are limited to simple designs [@westfallStatisticalPowerOptimal2014; @murayamaSummarystatisticsbasedPowerAnalysis2022], making it necessary to build data simulations tailored specifically to the study design. A number of tutorials have been published describing how to perform such simulation-based power analysis for multilevel models [@arendStatisticalPowerTwolevel2019; @lafitSelectionNumberParticipants2021; @zimmerSampleSizePlanning2023; @brysbaertPowerAnalysisEffect2018; @kumleEstimatingPowerGeneralized2021; @debruineUnderstandingMixedEffectsModels2021; @kainPracticalGuidePower2015; @greenSIMRPackagePower2016a; @johnsonPowerAnalysisGeneralized2015]. However, many of these tutorials focus on LMMs and the most common study designs [see @kumleEstimatingPowerGeneralized2021 for a tutorial that also covers more advanced settings]. This narrow focus provides limited guidance for researchers using more complex study designs, especially when little prior knowledge about plausible effect sizes is available [see the discussion in @kumleEstimatingPowerGeneralized2021]. Simulation-based power analysis with GLMMs requires making a range of assumptions about the model structure that should align with the characteristics of the data being analyzed. Existing tutorials often rely on heuristics for specifying variance components (e.g., the standard deviation of random intercepts) or assume that results from meta-analyses or data from pilot studies are available to determine plausible values for all model parameters. However, in practice, knowledge about those parameters from prior studies is often limited, which makes specifying assumptions a practical challenge (see the discussion in @maxwellSampleSizePlanning2008 and @kumleEstimatingPowerGeneralized2021). We will discuss a number of strategies on how to specify model parameters for application-specific, tailored data simulations in a later chapter.

@@

packagetable <- data.frame(
  col1 = c("glmmrBase", "longpower", "mixedpower", "mlmpower", "pamm", "pass.lme", "PowerAnalysisIL", "powerlmm", "simglm", "simr", "summary_statistics based_power", "WebPower"),
  col2 = c("Formula- and simulation-based power analysis; non-linear fixed effects and flexible covariance functions",
              "Formula-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; based on 'simr' package",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Formula-based power analysis; limited documentation",
              "Simulation-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Summary-statistics-based power analysis; based on 'pwr' package",
              "Formula-based power analysis; based on 'longpower' package; focus on longitudinal data"),
  col3 = c("no", "[yes](https://atrihub.shinyapps.io/power/)", "no", "no", "no", "no", "[yes](https://github.com/ginettelafit/PowerAnalysisIL?tab=readme-ov-file#shiny-app-and-r-package-to-perform-power-analysis-to-select-the-number-of-participants-in-intensive-longitudinal-studies)", "[yes](https://github.com/rpsychologist/powerlmm?tab=readme-ov-file#launch-interactive-web-application)", "[yes](https://simglm.brandonlebeau.org/reference/run_shiny.html)", "no", "[yes](https://koumurayama.shinyapps.io/summary_statistics_based_power/)", "[yes](https://webpower.psychstat.org/wiki/start)"),
  col4 = c("yes", "no", "yes", "no", "no", "no", "no", "no", "yes", "yes", "yes", "no"),
  col5 = c("none", "limited set of study designs with two levels", "none", "limited to two levels", "none", "none", "limited set of study designs with two levels", "limited set of study designs with two or three levels", "limited to two or three levels", "none", "limited set of study designs with two levels", "limited set of study designs with two levels"),
  col6 = c("@watsonGeneralisedLinearMixed2023", "@iddiPowerSampleSize2022", "@kumleEstimatingPowerGeneralized2021", "@endersSimpleMonteCarlo2023", "@martinMeasuringIndividualDifferences2011", "@marcochakyanyuPassLmePower2019", "@lafitSelectionNumberParticipants2021", "@magnussonConsequencesIgnoringTherapist2018", "@lebeauPowerAnalysisSimulation2019", "@greenSIMRPackagePower2016", "@murayamaSummarystatisticsbasedPowerAnalysis2022", "@zhangPracticalStatisticalPower2018")
)
names(packagetable) <- c("Package name", "Summary", "GUI available", "GLMM support", "Design limitations", "Reference")

@@

#### THEORY

@@

#### PRACTICE

@@

##### Our specific GLMM

In a GLMM, the expected value of the dependent variable $Y$ conditioned on the vector of predictor variables $\mathbf{X}$ and random effects $\mathbf{U}$, transformed by a link function $g()$ is modeled as a linear combination $\eta$ of the predictor variables $\mathbf{X}$, the random effects $\mathbf{U}$, and the model parameters $\mathbf{\beta}$ [@fahrmeirRegressionModelsMethods2021]: 
$$
g(E(Y|\mathbf{X}=\mathbf{x},\mathbf{U}=\mathbf{u})) = \eta
$$
Equivalently, the conditional expected value is modeled as the linear combination $\eta$, transformed by the inverse link function $g^{-1}()$: 
$$
E(Y|\mathbf{X}=\mathbf{x},\mathbf{U}=\mathbf{u}) = g^{-1}(\eta)
$$
If the dependent variable (i.e., diagnostic decision) $Y$ is a binary variable with values $0$ (i.e., inaccurate), or $1$ (i.e., accurate), the conditional expected value is equivalent to the probability: 
$$
P_{si} := P(Y = 1|\mathbf{X}=\mathbf{x},\mathbf{U}=\mathbf{u})
$$
In our case study, $P_{si}$ is the conditional probability that subject $s$ gives the correct response to item (i.e., CT scan) $i$.

@@

##### Simulation function in R

The following R function simulates a full dataset structured according to the design of our case study.

@@

@@

```{r}
#| label: fig-margdist2
#| echo: false
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of item random intercepts to 0.01."
set.seed(1)
dat <- simulate(n_subjects = 3000, n_items = 3000, sd_u0i = 0.01)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```
For the next plot, we have set the item standard deviation to almost zero ($\sigma_I = 0.01$). This gives us a better way to see the variability between persons. As an example, @fig-margdist2 reveals a number of implicit assumptions about the comparison between experts and students: With incorrect advice, virtually all experts have a higher probability of making a correct diagnosis compared to students when considering only items with average difficulty. In contrast, there is considerable overlap in probability between experts and students with no advice and even higher overlap with correct advice. Patterns like these should be considered carefully and discussed with the domain experts. Parameter values ($\beta$ parameters, and $\sigma_S$) should be adjusted if the implications do not seem reasonable.
We could also have a closer look at the variability between items by setting the subject standard deviation to almost zero ($\sigma_S = 0.01$).
```{r}
#| include: false
set.seed(1)
dat <- simulate(n_subjects = 3000, n_items = 3000, sd_u0s = 0.01)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

The final plot demonstrates that these plots are also useful for spotting standard deviations that were specified too high. For @fig-margdist3 we have set $\sigma_S = 3$ and $\sigma_I = 3$. This implies that in each experimental condition, the probabilities that a subject solves an item are overwhelmingly close to either 0 or 1 and nothing in between, which is not a plausible assumption. These high standard deviations do not account for the inherent variability and complexity of human performance. For example, the expectation that an expert with low ability and incorrect advice would solve a difficult item with a probability close to zero is not convincing.
```{r}
#| label: fig-margdist3
#| echo: false
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of subject and item random intercepts to 3."
set.seed(1)
dat <- simulate(n_subjects = 3000, n_items = 3000, sd_u0s = 3, sd_u0i = 3)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

@@

##### PRACTICE

@@

#### Hypothesis testing

If we chose hypothesis testing for our case study, we would test a combined null hypothesis $H_0$ that consists of four separate null hypotheses:
$$
\begin{aligned}
H_{01}:\ & P(Y=1|advice\_present = 1, advice\_correct = 1, expert = 1, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 1, u_{0s} = 0, u_{0i} = 0) \\
H_{02}:\ &P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 1, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 1, advice\_correct = 0, expert = 1, u_{0s} = 0, u_{0i} = 0) \\
H_{03}:\ &P(Y=1|advice\_present = 1, advice\_correct = 1, expert = 0, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 0, u_{0s} = 0, u_{0i} = 0) \\
H_{04}:\ & P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 0, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 1, advice\_correct = 0, expert = 0, u_{0s} = 0, u_{0i} = 0)
\end{aligned}
$$
The combined null hypothesis $H_0$ should only be rejected if **all** individual null hypotheses are rejected [i.e., intersection-union setting\; @dmitrienkoTraditionalMultiplicityAdjustment2013].
In such cases, the error probabilities do not accumulate, and we would waste power when correcting for multiple tests.

@@

#### Interval estimation

If we chose parameter estimation for our case study, we would focus on the two-sided CIs of the four contrasts of interest.
With a standard confidence level of $1 - \alpha = 0.95$ plausible values are clearly in the positive range for the first, third, and fourth contrast, while both negative and positive values seem plausible for the second contrast.
Note that due to the constrained range of the probability scale, the width of the CI differs between the four contrasts (which is the expected behavior for binomial GLMMs).
The smallest width is observed for the first contrast (expert with correct advice vs. expert without advice), where both underlying probabilities are close to 1.
The largest width is observed for the fourth contrast (student with incorrect advice vs. student without advice), where both underlying probabilities are closer to 0.5.

@@

#### Power results

For our exemplary combined hypothesis, power is defined as the (long-run) percentage of simulations in which all four p-values of our individual hypotheses are significant at the $\alpha = 0.05$ level. Based on our simulation outcomes, we compute a power estimate for each combination of `n_subjects` $\times$ `n_items` (including 95% CIs) and visualize the results with the following code.^[This code was inspired by the "Mixed Design Simulation" vignette of the *faux* package at <https://debruine.github.io/faux/articles/sim_mixed.html>.]

@@

#### Precision results

When planning for precision, one could monitor the width of all four CIs at the same time.
However, because the CIs of the four contrasts strongly differ in width, it is not trivial to decide which width one should target when deciding on the appropriate sample size.
In contrast to planning for power, there are no common standards on how to specify the targeted precision [@lakensSampleSizeJustification2022].
For our example, we use a simple heuristic but we strongly encourage readers to think about better alternatives that are appropriate in their own applications.
Our simulations show that the smallest CI can be expected for the first contrast (expert with correct advice vs. expert without advice).
The true contrast in probability for an average expert and an average item in this condition is `plogis(b_0 + b_e + b_a + b_c + b_ea + b_ec) - plogis(b_0 + b_e) =` $`r round(plogis(b_0 + b_e + b_a + b_c + b_ea + b_ec) - plogis(b_0 + b_e), 3)`$.
We want the width of this CI to be smaller than 0.1.
This would mean that if the point estimate happens to be close to the true value, the plausible values inside of a 95% CI would all be positive.

@@

## Step 7 (optional): Sensitivity analysis

>>>>

To our knowledge, existing approaches for sample size planning for GLMMs have exclusively focused on planning for power. In Table 1, we review available software packages that can be used to perform power analysis for multilevel models in `r cite_r()`. Power analysis methods can be categorized into formula-based, summary-statistics-based and simulation-based methods [@murayamaSummarystatisticsbasedPowerAnalysis2022]. Formula-based methods rely on exact formulas to calculate power directly. Summary-statistics-based methods use statistical theory to approximate power based on formula-based methods developed for simple t-tests. Simulation-based methods rely on repeatedly simulating data with a known true effect size and estimating power empirically, that is what percentage of simulated datasets produces a significant p-value.
Available formula-based and summary-statistics-based software packages for multilevel models often do not include GLMMs or are limited to simple designs [@westfallStatisticalPowerOptimal2014; @murayamaSummarystatisticsbasedPowerAnalysis2022], making it necessary to build data simulations tailored specifically to the study design. A number of tutorials have been published describing how to perform such simulation-based power analysis for multilevel models [@arendStatisticalPowerTwolevel2019; @lafitSelectionNumberParticipants2021; @zimmerSampleSizePlanning2023; @brysbaertPowerAnalysisEffect2018; @kumleEstimatingPowerGeneralized2021; @debruineUnderstandingMixedEffectsModels2021; @kainPracticalGuidePower2015; @greenSIMRPackagePower2016; @johnsonPowerAnalysisGeneralized2015]. However, many of these tutorials focus on LMMs and the most common study designs [see @kumleEstimatingPowerGeneralized2021 for a tutorial that also covers more advanced settings]. This narrow focus provides limited guidance for researchers using more complex study designs, especially when little prior knowledge about plausible effect sizes is available [see the discussion in @kumleEstimatingPowerGeneralized2021]. Simulation-based power analysis with GLMMs requires making a range of assumptions about the model structure that should align with the characteristics of the data being analyzed. Existing tutorials often rely on heuristics for specifying variance components (e.g., the standard deviation of random intercepts) or assume that results from meta-analyses or data from pilot studies are available to determine plausible values for all model parameters. However, in practice, knowledge about those parameters from prior studies is often limited, which makes specifying assumptions a practical challenge (see the discussion in @maxwellSampleSizePlanning2008 and @kumleEstimatingPowerGeneralized2021). We will discuss a number of strategies on how to specify model parameters for application-specific, tailored data simulations in a later chapter.

@@

packagetable <- data.frame(
  col1 = c("glmmrBase", "longpower", "mixedpower", "mlmpower", "pamm", "pass.lme", "PowerAnalysisIL", "powerlmm", "simglm", "simr", "summary_statistics based_power", "WebPower"),
  col2 = c("Formula- and simulation-based power analysis; non-linear fixed effects and flexible covariance functions",
              "Formula-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; based on 'simr' package",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Formula-based power analysis; limited documentation",
              "Simulation-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Summary-statistics-based power analysis; based on 'pwr' package",
              "Formula-based power analysis; based on 'longpower' package; focus on longitudinal data"),
  col3 = c("no", "[yes](https://atrihub.shinyapps.io/power/)", "no", "no", "no", "no", "[yes](https://github.com/ginettelafit/PowerAnalysisIL?tab=readme-ov-file#shiny-app-and-r-package-to-perform-power-analysis-to-select-the-number-of-participants-in-intensive-longitudinal-studies)", "[yes](https://github.com/rpsychologist/powerlmm?tab=readme-ov-file#launch-interactive-web-application)", "[yes](https://simglm.brandonlebeau.org/reference/run_shiny.html)", "no", "[yes](https://koumurayama.shinyapps.io/summary_statistics_based_power/)", "[yes](https://webpower.psychstat.org/wiki/start)"),
  col4 = c("yes", "no", "yes", "no", "no", "no", "no", "no", "yes", "yes", "yes", "no"),
  col5 = c("none", "limited set of study designs with two levels", "none", "limited to two levels", "none", "none", "limited set of study designs with two levels", "limited set of study designs with two or three levels", "limited to two or three levels", "none", "limited set of study designs with two levels", "limited set of study designs with two levels"),
  col6 = c("@watsonGeneralisedLinearMixed2023", "@iddiPowerSampleSize2022", "@kumleEstimatingPowerGeneralized2021", "@endersSimpleMonteCarlo2023", "@martinMeasuringIndividualDifferences2011", "@yumarcoPassLmePower2019", "@lafitSelectionNumberParticipants2021", "@magnussonConsequencesIgnoringTherapist2018", "@lebeauPowerAnalysisSimulation2019", "@greenSIMRPackagePower2016", "@murayamaSummarystatisticsbasedPowerAnalysis2022", "@zhangPracticalStatisticalPower2018")
)
names(packagetable) <- c("Package name", "Summary", "GUI available", "GLMM support", "Design limitations", "Reference")

@@

@@

@@

**Our specific GLMM.** In a GLMM, the expected value of the dependent variable $Y$ conditioned on the vector of predictor variables $\mathbf{X}$ and random effects $\mathbf{U}$, transformed by a link function $g()$ is modeled as a linear combination $\eta$ of the predictor variables $\mathbf{X}$, the random effects $\mathbf{U}$, and the model parameters $\mathbf{\beta}$ [@fahrmeirRegressionModelsMethods2021]: 
$$
g(E(Y|\mathbf{X}=\mathbf{x},\mathbf{U}=\mathbf{u})) = \eta
$$
Equivalently, the conditional expected value is modeled as the linear combination $\eta$, transformed by the inverse link function $g^{-1}()$: 
$$
E(Y|\mathbf{X}=\mathbf{x},\mathbf{U}=\mathbf{u}) = g^{-1}(\eta)
$$
If the dependent variable (i.e., diagnostic decision) $Y$ is a binary variable with values $0$ (i.e., inaccurate), or $1$ (i.e., accurate), the conditional expected value is equivalent to the probability: 
$$
P_{si} := P(Y = 1|\mathbf{X}=\mathbf{x},\mathbf{U}=\mathbf{u})
$$
In our case study, $P_{si}$ is the conditional probability that subject $s$ gives the correct response to item (i.e., CT scan) $i$.

@@

**Simulation function in R.** The following R function simulates a full dataset structured according to the design of our case study.

@@

\newpage

@@

```{r}
#| label: fig-margdist2
#| echo: false
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of item random intercepts to 0.01."
set.seed(1)
dat <- simulate(n_subjects = 3000, n_items = 3000, sd_u0i = 0.01)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```
For the next plot, we have set the item standard deviation to almost zero ($\sigma_I = 0.01$). This gives us a better way to see the variability between persons. As an example, @fig-margdist2 reveals a number of implicit assumptions about the comparison between experts and students: With incorrect advice, virtually all experts have a higher probability of making a correct diagnosis compared to students when considering only items with average difficulty. In contrast, there is considerable overlap in probability between experts and students with no advice and even higher overlap with correct advice. Patterns like these should be considered carefully and discussed with the domain experts. Parameter values ($\beta$ parameters, and $\sigma_S$) should be adjusted if the implications do not seem reasonable.  
The final plot demonstrates that these plots are also useful for spotting standard deviations that were specified too high. For @fig-margdist3 we have set $\sigma_S = 3$ and $\sigma_I = 3$. This implies that in each experimental condition, the probabilities that a subject solves an item are overwhelmingly close to either 0 or 1 and nothing in between, which is not a plausible assumption. These high standard deviations do not account for the inherent variability and complexity of human performance. For example, the expectation that an expert with low ability and incorrect advice would solve a difficult item with a probability close to zero is not convincing.
```{r}
#| label: fig-margdist3
#| echo: false
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of subject and item random intercepts to 3."
set.seed(1)
dat <- simulate(n_subjects = 3000, n_items = 3000, sd_u0s = 3, sd_u0i = 3)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

@@

@@

**Hypothesis testing.** If we chose hypothesis testing for our case study, we would test a combined null hypothesis $H_0$ that consists of four separate null hypotheses:
$$
\begin{aligned}
H_{01}:\ & P(Y=1|advice\_present = 1, advice\_correct = 1, expert = 1, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 1, u_{0s} = 0, u_{0i} = 0) \\
H_{02}:\ &P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 1, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 1, advice\_correct = 0, expert = 1, u_{0s} = 0, u_{0i} = 0) \\
H_{03}:\ &P(Y=1|advice\_present = 1, advice\_correct = 1, expert = 0, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 0, u_{0s} = 0, u_{0i} = 0) \\
H_{04}:\ & P(Y=1|advice\_present = 0, advice\_correct = 0, expert = 0, u_{0s} = 0, u_{0i} = 0) \leq \\
& P(Y=1|advice\_present = 1, advice\_correct = 0, expert = 0, u_{0s} = 0, u_{0i} = 0)
\end{aligned}
$$
The combined null hypothesis $H_0$ should only be rejected if **all** individual null hypotheses are rejected [i.e., intersection-union setting\; @dmitrienkoTraditionalMultiplicityAdjustment2013].
In such cases, the error probabilities do not accumulate, and we would waste power when correcting for multiple tests.

@@

**Interval estimation.** If we chose parameter estimation for our case study, we would focus on the two-sided CIs of the four contrasts of interest.
With a standard confidence level of $1 - \alpha = 0.95$ plausible values are clearly in the positive range for the first, third, and fourth contrast, while both negative and positive values seem plausible for the second contrast.
Note that due to the constrained range of the probability scale, the width of the CI differs between the four contrasts (which is the expected behavior for binomial GLMMs).
The smallest width is observed for the first contrast (expert with correct advice vs. expert without advice), where both underlying probabilities are close to 1.
The largest width is observed for the fourth contrast (student with incorrect advice vs. student without advice), where both underlying probabilities are closer to 0.5.

@@

**Power results.** For our exemplary combined hypothesis, power is defined as the (long-run) percentage of simulations in which all four p-values of our individual hypotheses are significant at the $\alpha = 0.05$ level. Based on our simulation outcomes, we compute a power estimate for each combination of `n_subjects` $\times$ `n_items` (including 95% CIs) and visualize the results with the following code.^[This code was inspired by the "Mixed Design Simulation" vignette of the *faux* package at <https://debruine.github.io/faux/articles/sim_mixed.html>.]

@@

**Precision results.** When planning for precision, one could monitor the width of all four CIs at the same time.
However, because the CIs of the four contrasts strongly differ in width, it is not trivial to decide which width one should target when deciding on the appropriate sample size.
In contrast to planning for power, there are no common standards on how to specify the targeted precision [@lakensSampleSizeJustification2022].
For our example, we use a simple heuristic but we strongly encourage readers to think about better alternatives that are appropriate in their own applications.
Our simulations show that the smallest CI can be expected for the first contrast (expert with correct advice vs. expert without advice).
The true contrast in probability for an average expert and an average item in this condition is `plogis(b_0 + b_e + b_a + b_c + b_ea + b_ec) - plogis(b_0 + b_e) =` $`r round(plogis(b_0 + b_e + b_a + b_c + b_ea + b_ec) - plogis(b_0 + b_e), 3)`$.
We want the width of this CI to be smaller than 0.1.
This would mean that if the point estimate happens to be close to the true value, the plausible values inside of a 95% CI would all be positive.

@@

## Step 7 (optional): Conduct sensitivity analysis
